\bf Visual diagnostics for constrained optimisation with application to guided tours

### 2020-11-15 paper/paper.Rmd
Updating section 2

In this paper we focus on unconstrained optimization as defined in the introduction section and assume that it is not possible to find an analytical solution in closed form. That is, our problem consists of finding the mininum of a function $f \in L^p$ in the unconstrained $\mathbb{R}$ space.  In this scenario, gradient descent methods have taken the stage for many decades now. In gradient descent methods the goal is to find the mininum of an objective function, and the way to do so, is by taken steps  proportional to the negative gradient of the function at the evaluation point, that is $x_{k+1} = x_k -\alpha_kS_k$ where $\alpha_k$ is the step size or the learning rate (REF). The step size is the key in the success of the optimization problem as inadequate step sizes might lead to a failure in convergence. In order to solve this problem line minimization or line search methods were proposed (REF) where the step size is chosen in such a way that convergence is ensured. In line search methods users are required to provide an initial estimate $x_{1}$ and then for each iteration a search direction is established $S_k$ then the objective is to find the value of $\alpha_k \in \mathbb{R}$ that minimizes $f(x_k + \alpha_kS_k)$ with respect to $\alpha_k$ (this step is called the line sear). Then move on to the next pont following $x_{k+1} = x_k + \nu_kS_k$
\todo[inline]{lconnection with derivative free methods}

 **From Fletcher's book next paragraph --> clean up** Theoretical results have demonstrated the global convergence of the algorithm when the step-size $\alpha_k$ is chosen by minimising  $f(x^{(j)} + \alpha* d^{(j)})$ [@curry1944method]. This is however rarely implemented in practice, either because of the high computational demand or because the solution does not exist [@fletcher2013practical]. A modified approach, in the case of maximisation, is to impose a mandatory increase in the objective function for each iteration: $f^{(j+1)}> f^{(j)}$. Similarly, for  minimisation we would require a decrease in function value at each step. This approach turns out to be efficient in practical problems, but global convergence cannot be guaranteed in this case.

Modern development of line search methods focuses on improving the computation of the searching direction $S_{(j)}$, and on approximations of the step size $\alpha_j$, catering for practical optimisation problems. Here we focus on optimisation methods used with the projection pursuit guided tour described in the next section.

\todo[inline, color = pink]{Question for Sherry --> which implementaion is your search better? search better random? and search geodesic?}

\todo[inline]{line search--> search better,  search geodesic}

>>>>

In this paper we focus on unconstrained optimization as defined in the introduction section and assume that it is not possible to find an analytical solution in closed form. That is, our problem consists of finding the minimum of a function $f \in L^p$ in the unconstrained $\mathbb{R}$ space.  In this scenario, gradient descent methods have taken the stage for many decades now. In gradient descent methods the goal is to find the minimum of an objective function, and the way to do so, is by taken steps  proportional to the negative gradient of the function at the evaluation point, that is $x_{k+1} = x_k -\alpha_kS_k$ where $\alpha_k$ is the step size or the learning rate (REF). The step size is the key in the success of the optimization problem as inadequate step sizes might lead to a failure in convergence. In order to solve this problem line minimization or line search methods were proposed (REF) where the step size is chosen in such a way that convergence is ensured. In line search methods users are required to provide an initial estimate $x_{1}$ and then for each iteration a search direction $S_k$ is established then the objective is to find the value of $\alpha_k \in \mathbb{R}$ that minimizes $f(x_k + \alpha_kS_k)$ with respect to $\alpha_k$ (this step is called the line search). Then move on to the next point following $x_{k+1} = x_k + \alpha_kS_k$.
Modern development of line search methods focuses on improving the computation of the searching direction $S_{(k)}$, and on approximations of the step size $\alpha_k$, catering for practical optimisation problems. Here we focus on optimisation methods used with the projection pursuit guided tour described in the next section.

Derivative free --> adding

 <!-- **From Fletcher's book next paragraph --> clean up** Theoretical results have -->
 <!-- demonstrated the global convergence of the algorithm when the step-size -->
 <!-- $\alpha_k$ is chosen by minimising  $f(x^{(j)} + \alpha* d^{(j)})$ -->
 <!-- [@curry1944method]. This is however rarely implemented in practice, either -->
 <!-- because of the high computational demand or because the solution does not exist -->
 <!-- [@fletcher2013practical]. A modified approach, in the case of maximisation, is -->
 <!-- to impose a mandatory increase in the objective function for each iteration: -->
 <!-- $f^{(j+1)}> f^{(j)}$. Similarly, for  minimisation we would require a decrease -->
 <!-- in function value at each step. This approach turns out to be efficient in -->
 <!-- practical problems, but global convergence cannot be guaranteed in this case. -->

### 2020-11-15 paper/paper.tex
Updating section 2

In this paper we focus on unconstrained optimization as defined in the introduction section and assume that it is not possible to find an analytical solution in closed form. That is, our problem consists of finding the mininum of a function \(f \in L^p\) in the unconstrained \(\mathbb{R}\) space. In this scenario, gradient descent methods have taken the stage for many decades now. In gradient descent methods the goal is to find the mininum of an objective function, and the way to do so, is by taken steps proportional to the negative gradient of the function at the evaluation point, that is \(x_{k+1} = x_k -\alpha_kS_k\) where \(\alpha_k\) is the step size or the learning rate (REF). The step size is the key in the success of the optimization problem as inadequate step sizes might lead to a failure in convergence. In order to solve this problem line minimization or line search methods were proposed (REF) where the step size is chosen in such a way that convergence is ensured. In line search methods users are required to provide an initial estimate \(x_{1}\) and then for each iteration a search direction is established \(S_k\) then the objective is to find the value of \(\alpha_k \in \mathbb{R}\) that minimizes \(f(x_k + \alpha_kS_k)\) with respect to \(\alpha_k\) (this step is called the line sear). Then move on to the next pont following \(x_{k+1} = x_k + \nu_kS_k\)
\todo[inline]{lconnection with derivative free methods}

\textbf{From Fletcher's book next paragraph --\textgreater{} clean up} Theoretical results have demonstrated the global convergence of the algorithm when the step-size \(\alpha_k\) is chosen by minimising \(f(x^{(j)} + \alpha* d^{(j)})\) \citep{curry1944method}. This is however rarely implemented in practice, either because of the high computational demand or because the solution does not exist \citep{fletcher2013practical}. A modified approach, in the case of maximisation, is to impose a mandatory increase in the objective function for each iteration: \(f^{(j+1)}> f^{(j)}\). Similarly, for minimisation we would require a decrease in function value at each step. This approach turns out to be efficient in practical problems, but global convergence cannot be guaranteed in this case.

Modern development of line search methods focuses on improving the computation of the searching direction \(S_{(j)}\), and on approximations of the step size \(\alpha_j\), catering for practical optimisation problems. Here we focus on optimisation methods used with the projection pursuit guided tour described in the next section.

\todo[inline, color = pink]{Question for Sherry --> which implementaion is your search better? search better random? and search geodesic?}

\todo[inline]{line search--> search better,  search geodesic}

>>>>

In this paper we focus on unconstrained optimization as defined in the introduction section and assume that it is not possible to find an analytical solution in closed form. That is, our problem consists of finding the minimum of a function \(f \in L^p\) in the unconstrained \(\mathbb{R}\) space. In this scenario, gradient descent methods have taken the stage for many decades now. In gradient descent methods the goal is to find the minimum of an objective function, and the way to do so, is by taken steps proportional to the negative gradient of the function at the evaluation point, that is \(x_{k+1} = x_k -\alpha_kS_k\) where \(\alpha_k\) is the step size or the learning rate (REF). The step size is the key in the success of the optimization problem as inadequate step sizes might lead to a failure in convergence. In order to solve this problem line minimization or line search methods were proposed (REF) where the step size is chosen in such a way that convergence is ensured. In line search methods users are required to provide an initial estimate \(x_{1}\) and then for each iteration a search direction \(S_k\) is established then the objective is to find the value of \(\alpha_k \in \mathbb{R}\) that minimizes \(f(x_k + \alpha_kS_k)\) with respect to \(\alpha_k\) (this step is called the line search). Then move on to the next point following \(x_{k+1} = x_k + \alpha_kS_k\).
Modern development of line search methods focuses on improving the computation of the searching direction \(S_{(k)}\), and on approximations of the step size \(\alpha_k\), catering for practical optimisation problems. Here we focus on optimisation methods used with the projection pursuit guided tour described in the next section.

Derivative free --\textgreater{} adding

clean up** Theoretical results have --\textgreater{}
